Actuator line modeling of vertical-axis turbines

### 2016-05-02 paper.tex
Use past tense

    \caption{Actuator line geometry. Filled circles indicate points where
    geometry is defined whereas squares indicate actuator line element
    quarter-chord locations. Chord mount offset is defined as the distance from
    an element's leading edge to each geometry point in chord lengths, which is
    0.5 for both turbines in this study.}

>>>>

    \caption{Actuator line geometry. Filled circles indicate points where
    geometry is defined whereas squares indicate actuator line element
    quarter-chord locations. Chord mount offset is defined as the distance from
    an element's leading edge to each geometry point in chord lengths, which was
    0.5 for both rotors modeled in this study.}
